Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-05-04 doc/RMD/mlg-mcg.Rmd
change scale

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% mcgs$MCG[1:5])
top5g <- make_mcgmlg_graph(top5)
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
set.seed(2017-05-03)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "nicely")
mcg_mlg_graph %+% top5lay + ggtitle("Top 5 Mycelial Compatibility Groups and associated MLGs")
```

>>>>

```{r top5graph, fig.height = 7, fig.width = 7}
top5 <- filter(mcgmlg, as.character(MCG) %in% mcgs$MCG[1:5])
top5g <- make_mcgmlg_graph(top5)
tosize <- V(top5g)$size
V(top5g)$size <- sqrt(tosize)/10
set.seed(2017-05-03)
top5lay <- create_layout(top5g, layout = "igraph", algorithm = "nicely")
t5g <- mcg_mlg_graph %+% top5lay + ggtitle("Top 5 Mycelial Compatibility Groups and associated MLGs")
ggsave(t5g, file = file.path("results", "figures", "publication", "FigureS2B.svg"), width = 88, height = 88, scale = 3, units = "mm")
```
